### 2018-11-14 sections/conclusion.tex
Partly implemented D. Stoker's CDS comments

A search for flavour-changing neutral current decays of a top quark into an up-type quark ($q=u, c$) and the Standard Model Higgs boson, $t\to Hq$, is presented. 
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016 with the ATLAS detector at the 
CERN Large Hadron Collider and corresponds to an integrated luminosity of 36.1 fb$^{-1}$.
Two complementary analyses are performed that search for top-quark pair events in which one top quark decays into $Wb$ and the other top quark decays into $Hq$,
and target the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$  decay modes, respectively.  
The $\Hbb$ search selects events with one isolated electron or muon from the $W \to \ell\nu$ decay, and multiple jets, with several 
of them being identified with high purity as originating from the hadronisation of $b$-quarks. 
The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well as multiple jets. 
Both searches employ multivariate techniques to discriminate between the signal and the background on the basis of their different kinematics. 
No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to Hq$ branching ratios are derived.
In the case of the $\Hbb$ search, the observed (expected) 95\% CL upper limits on the on the $t\to Hc$ and $t\to Hu$ branching ratios 
are $4.2 \times 10^{-3}\,(4.0 \times 10^{-3})$ and $5.2 \times 10^{-3}\,(4.9 \times 10^{-3})$, respectively.
In the case of the $\Htautau$ search, the observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios 
are $1.9 \times 10^{-3}\,(2.1 \times 10^{-3})$ and $1.7 \times 10^{-3}\,(2.0 \times 10^{-3})$, respectively.
The combination of these searches with ATLAS searches in diphoton and multilepton final states 
%significantly improves the sensitivity, 
yields observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of $1.1 \times 10^{-3}$ ($8.3 \times 10^{-4}$) 
and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$), assuming respectively $\BR(t\to Hu)=0$ and $\BR(t\to Hc)=0$.
The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 
%Upper limits in the $t\to Hc$ versus $t\to Hu$ branching ratio plane, as well as best-fit branching ratios, are also reported.
These are the most restrictive direct bounds on $tqH$ ($q=u,c$) interactions obtained so far.

>>>>

A search for flavour-changing neutral-current decays of a top quark into an up-type quark ($q=u, c$) and the Standard Model Higgs boson, $t\to Hq$, is presented. 
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016 with the ATLAS detector at the 
CERN Large Hadron Collider and corresponding to an integrated luminosity of 36.1 fb$^{-1}$.
Two complementary analyses are performed to search for top-quark pair events in which one top quark decays into $Wb$ and the other top quark decays into $Hq$,
and target the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$  decay modes, respectively.  
The $\Hbb$ search selects events with one isolated electron or muon from the $W \to \ell\nu$ decay, and multiple jets, with several 
of them being identified with high purity as originating from the hadronisation of $b$-quarks. 
The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well as multiple jets. 
Both searches employ multivariate techniques to discriminate between the signal and the background on the basis of their different kinematics. 
No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to Hq$ branching ratios are derived.
In the case of the $\Hbb$ search, the observed (expected) 95\% CL upper limits on the on the $t\to Hc$ and $t\to Hu$ branching ratios 
are $4.2 \times 10^{-3}\,(4.0 \times 10^{-3})$ and $5.2 \times 10^{-3}\,(4.9 \times 10^{-3})$, respectively.
In the case of the $\Htautau$ search, the observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios 
are $1.9 \times 10^{-3}\,(2.1 \times 10^{-3})$ and $1.7 \times 10^{-3}\,(2.0 \times 10^{-3})$, respectively.
The combination of these searches with ATLAS searches in diphoton and multilepton final states 
%significantly improves the sensitivity, 
yields observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of $1.1 \times 10^{-3}$ ($8.3 \times 10^{-4}$) 
and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$), assuming respectively $\BR(t\to Hu)=0$ and $\BR(t\to Hc)=0$.
The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 
%Upper limits in the $t\to Hc$ versus $t\to Hu$ branching ratio plane, as well as best-fit branching ratios, are also reported.
These are the most restrictive direct bounds on $tqH$ ($q=u,c$) interactions obtained so far.

### 2018-11-14 sections/detector.tex
Partly implemented D. Stoker's CDS comments

The ATLAS detector~\cite{PERF-2007-01} at the LHC covers almost the entire solid angle around the collision point,\footnote{ATLAS 
uses a right-handed coordinate system with its origin at the nominal interaction point (IP) in the 
centre of the detector.  
%and the $z$-axis coinciding with the axis of the beam pipe.
The $x$-axis points from
the IP to the centre of the LHC ring, %and
the $y$-axis points upward,
and the $z$-axis coincides with the axis of the beam pipe.
Cylindrical coordinates ($r$,$\phi$) are used 
in the transverse plane, $\phi$ being the azimuthal angle around the beam pipe. The pseudorapidity is defined in 
terms of the polar angle $\theta$ as $\eta = - \ln \tan(\theta/2)$.
Angular distance is measured in units of $\Delta R\equiv \sqrt{(\Delta\eta)^2+(\Delta\phi)^2}$.} and
consists of an inner tracking detector surrounded by a thin superconducting solenoid producing a
2~T axial magnetic field, electromagnetic and hadronic calorimeters, and a muon spectrometer
incorporating three large toroid magnet assemblies. The inner detector consists of a high-granularity silicon pixel detector, 
including the %newly-installed
insertable B-layer~\cite{IBL}, installed in 2014,
and a silicon microstrip tracker,
together providing a precise reconstruction of tracks of charged particles in the pseudorapidity range $|\eta|<2.5$.
The inner detector also includes a transition radiation tracker that provides tracking and electron identification for $|\eta|<2.0$.
%The electromagnetic (EM) sampling calorimeter uses lead as the absorber material 
%and liquid-argon (LAr) as the active medium, and is divided into barrel ($|\eta|<1.475$) and end-cap ($1.375<|\eta|<3.2$) regions.  
%Hadron calorimetry is also based on the sampling technique, with either scintillator tiles or LAr as the active medium, and with 
%steel, copper, or tungsten as the absorber material. The calorimeters cover $|\eta|<4.9$. 
%Hadronic calorimetry is provided by the steel/scintillating-tile calorimeter,
%segmented into three barrel structures within $|\eta| < 1.7$, and two copper/LAr hadronic endcap calorimeters.
%The solid angle coverage is completed with forward copper/LAr and tungsten/LAr calorimeter modules
%optimised for electromagnetic and hadronic measurements respectively.
The calorimeter system covers the pseudorapidity range $|\eta| < 4.9$.
Within the region $|\eta|< 3.2$, electromagnetic (EM) calorimetry is provided by barrel and 
endcap high-granularity lead/liquid-argon (LAr) sampling calorimeters,
with an additional thin LAr presampler covering $|\eta| < 1.8$,
to correct for energy loss in material upstream of the calorimeters.
Hadronic calorimetry is provided by %the
a steel/scintillator-tile calorimeter,
segmented into three barrel structures within $|\eta| < 1.7$, and two copper/LAr hadronic endcap calorimeters.
The solid angle coverage is completed with forward copper/LAr and tungsten/LAr calorimeter modules
optimised for electromagnetic and hadronic measurements, respectively.
The calorimeters are surrounded by a muon spectrometer within a magnetic field provided by air-core toroid magnets 
with a bending integral of about 2.5 Tm in the barrel and up to 6 Tm in the end-caps. 
The muon spectrometer measures the trajectories of muons with $|\eta|<2.7$ using multiple layers of high-precision tracking chambers,
and is instrumented with separate trigger chambers covering $|\eta|<2.4$.
A two-level trigger system~\cite{Aaboud:2016leb}, consisting of a hardware-based level-1 trigger followed by 
a software-based high-level trigger, is used to reduce the event rate to a maximum of around 1 kHz for offline storage.

>>>>

The ATLAS detector~\cite{PERF-2007-01} at the LHC covers almost the entire solid angle around the collision point,\footnote{ATLAS 
uses a right-handed coordinate system with its origin at the nominal interaction point (IP) in the 
centre of the detector.  
%and the $z$-axis coinciding with the axis of the beam pipe.
The $x$-axis points from
the IP to the centre of the LHC ring, %and
the $y$-axis points upward,
and the $z$-axis coincides with the axis of the beam pipe.
Cylindrical coordinates ($r$,$\phi$) are used 
in the transverse plane, $\phi$ being the azimuthal angle around the beam pipe. The pseudorapidity is defined in 
terms of the polar angle $\theta$ as $\eta = - \ln \tan(\theta/2)$.
Angular distance is measured in units of $\Delta R\equiv \sqrt{(\Delta\eta)^2+(\Delta\phi)^2}$.} and
consists of an inner tracking detector surrounded by a thin superconducting solenoid producing a
2~T axial magnetic field, electromagnetic and hadronic calorimeters, and a muon spectrometer
incorporating three large toroid magnet assemblies. The inner detector consists of a high-granularity silicon pixel detector, 
including the %newly-installed
insertable B-layer~\cite{IBL}, installed in 2014,
and a silicon microstrip tracker,
together providing a precise reconstruction of tracks of charged particles in the pseudorapidity range $|\eta|<2.5$.
The inner detector also includes a transition radiation tracker that provides tracking and electron identification for $|\eta|<2.0$.
%The electromagnetic (EM) sampling calorimeter uses lead as the absorber material 
%and liquid-argon (LAr) as the active medium, and is divided into barrel ($|\eta|<1.475$) and end-cap ($1.375<|\eta|<3.2$) regions.  
%Hadron calorimetry is also based on the sampling technique, with either scintillator tiles or LAr as the active medium, and with 
%steel, copper, or tungsten as the absorber material. The calorimeters cover $|\eta|<4.9$. 
%Hadronic calorimetry is provided by the steel/scintillating-tile calorimeter,
%segmented into three barrel structures within $|\eta| < 1.7$, and two copper/LAr hadronic endcap calorimeters.
%The solid angle coverage is completed with forward copper/LAr and tungsten/LAr calorimeter modules
%optimised for electromagnetic and hadronic measurements respectively.
The calorimeter system covers the pseudorapidity range $|\eta| < 4.9$.
Within the region $|\eta|< 3.2$, electromagnetic (EM) calorimetry is provided by barrel and 
endcap high-granularity lead/liquid-argon (LAr) sampling calorimeters,
with an additional thin LAr presampler covering $|\eta| < 1.8$,
to correct for energy loss in material upstream of the calorimeters.
Hadronic calorimetry is provided by %the
a steel/scintillator-tile calorimeter,
segmented into three barrel structures within $|\eta| < 1.7$, and two copper/LAr hadronic endcap calorimeters.
The solid angle coverage is completed with forward copper/LAr and tungsten/LAr calorimeter modules
optimised for electromagnetic and hadronic measurements, respectively.
The calorimeters are surrounded by a muon spectrometer within a magnetic field provided by air-core toroid magnets 
with a bending integral of about 2.5 Tm in the barrel and up to 6 Tm in the endcaps. 
The muon spectrometer measures the trajectories of muons with $|\eta|<2.7$ using multiple layers of high-precision tracking chambers,
and is instrumented with separate trigger chambers covering $|\eta|<2.4$.
A two-level trigger system~\cite{Aaboud:2016leb}, consisting of a hardware-based level-1 trigger followed by 
a software-based high-level trigger, is used to reduce the event rate to a maximum of around 1 kHz for offline storage.

### 2018-11-14 sections/strategy_Hbb.tex
Partly implemented D. Stoker's CDS comments

Given the choice of the $W\to\ell\nu$ and $H\to b\bar{b}$ decay modes, the $\ttbar \to WbHq$ signal 
is expected to have four jets in the final state, three of them originating from $b$-quarks, which 
can be effectively exploited to suppress the background. 
Additional jets can also be present because of initial- or final-state radiation.
However, the use of the 60\% $b$-tagging efficiency operating point, characterised by a low mistag rate for
charm and light jets, results in both $\Hc$ and $\Hu$ signals having a similar $b$-tag multiplicity distribution,
with a very small fraction of events having four or more $b$-tagged jets.

@@

The overall rate and composition of the $\ttbar$+jets background strongly depends on the jet and $b$-tag 
multiplicities, as illustrated in Figure~\ref{fig:Hbb_Summary}.
Regions with exactly two $b$-tagged jets are dominated by $\ttbar$+light-jets, while regions with 
at least four $b$-tagged jets are dominated by \ttbin. Intermediate compositions are found in regions with exactly three 
$b$-tagged jets.  Most of the $\ttbar$+light-jets background events in these regions have a charm jet from the hadronic $W$ boson 
decay  being $b$-tagged, in addition to the two $b$-jets from the top quark decays.

@@

This search uses a similar likelihood (LH) discriminant as that developed in Ref.~\cite{Aad:2015pja}.
The LH variable for a given event is defined as:
\begin{equation*}
LH(\mathbf{x}) = \frac{P^\textrm{sig}(\mathbf{x}) }{P^\textrm{sig}(\mathbf{x}) +P^\textrm{bkg}(\mathbf{x}) },
\label{eq:D}
\end{equation*}
where $P^\textrm{sig}(\mathbf{x}) $ and $P^\textrm{bkg}(\mathbf{x}) $ represent the probability density functions (pdf) of a given event under
the signal hypothesis ($\ttbar \to WbHq$) and under the background hypothesis ($\ttbar \to WbWb$), respectively.
Both $P^\textrm{sig}$ and $P^\textrm{bkg}$ are functions of $\mathbf{x}$, which denotes the set of two-body and three-body invariant masses 
that correspond to the expected resonances in the event (the leptonically decaying $W$ boson, the Higgs boson or the hadronically 
decaying $W$ boson, and the corresponding parent top quarks). These invariant masses are computed from the reconstructed 
lepton, jets, and missing transverse momentum.
As in Ref.~\cite{Aad:2015pja}, $P^\textrm{sig}$ and $P^\textrm{bkg}$ are approximated as a product of one-dimensional pdfs for
each of the invariant masses considered, and averaged among all possible parton--jet matching combinations. 
Combinations are weighted using information on the per-jet multivariate $b$-tagging discriminant value to suppress the impact from 
parton--jet assignments that are inconsistent with the correct parton candidates flavour.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[htbp]
\begin{center}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_lep0_pt.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_met.eps}} \\
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_hthad.eps}} 
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_mbb_mindR.eps}} \\ 
\caption{\small{$\Hbb$ search: Comparison between the data and background prediction for several kinematic 
distributions in the (4j, 3b) region before the fit to data (``Pre-Fit''). 
The distributions are shown for (a) lepton $\pt$, (b) $\met$, (c) scalar sum of the transverse momenta of 
the jets ($\hthad$), and (d) the invariant mass of the two $b$-tagged jets with lowest 
$\Delta R$ separation ($\mbb$).
The small contributions from $\ttbar V$, $\ttbar H$, single top, $W/Z$+jets, diboson, and multijet backgrounds are combined 
into a single background source referred to as ``Non-$\ttbar$''. 
The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
added to the background prediction.
The last bin in all figures contains the overflow.
The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction. 
The blue triangles indicate points that are outside the vertical range of the figure. 
The hashed area represents the total uncertainty of the background, excluding the normalisation uncertainty of the $\ttbin$ background, 
which is determined via a likelihood fit to data.}}
\label{fig:Hbb_extravars_4j3b}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

Given the choice of the $W\to\ell\nu$ and $H\to b\bar{b}$ decay modes, the $\ttbar \to WbHq$ signal 
is expected to have four jets in the final state, three of them originating from $b$-quarks, which 
can be effectively exploited to suppress the background. 
Additional jets can also be present because of initial- or final-state radiation.
However, the use of the 60\% $b$-tagging efficiency operating point, characterised by a low mistag rate for
$c$- and light-jets, results in both $\Hc$ and $\Hu$ signals having a similar $b$-tag multiplicity distribution,
with a very small fraction of events having four or more $b$-tagged jets.

@@

The overall rate and composition of the $\ttbar$+jets background strongly depends on the jet and $b$-tag 
multiplicities, as illustrated in Figure~\ref{fig:Hbb_Summary}.
Regions with exactly two $b$-tagged jets are dominated by $\ttbar$+light-jets, while regions with 
at least four $b$-tagged jets are dominated by \ttbin. Intermediate compositions are found in regions with exactly three 
$b$-tagged jets.  Most of the $\ttbar$+light-jets background events in these regions have a charm jet from the hadronic $W$ boson 
decay  being $b$-tagged, in addition to the two $b$-jets from the top-quark decays.

@@

This search uses a similar likelihood (LH) discriminant as that developed in Ref.~\cite{Aad:2015pja}.
The LH variable for a given event is defined as:
\begin{equation*}
L(\mathbf{x}) = \frac{P^\textrm{sig}(\mathbf{x}) }{P^\textrm{sig}(\mathbf{x}) +P^\textrm{bkg}(\mathbf{x}) },
\label{eq:D}
\end{equation*}
where $P^\textrm{sig}(\mathbf{x}) $ and $P^\textrm{bkg}(\mathbf{x}) $ represent the probability density functions (pdf) of a given event under
the signal hypothesis ($\ttbar \to WbHq$) and under the background hypothesis ($\ttbar \to WbWb$), respectively.
Both $P^\textrm{sig}$ and $P^\textrm{bkg}$ are functions of $\mathbf{x}$, which denotes the set of two-body and three-body invariant masses 
that correspond to the expected resonances in the event (the leptonically decaying $W$ boson, the Higgs boson or the hadronically 
decaying $W$ boson, and the corresponding parent top quarks). These invariant masses are computed from the reconstructed 
lepton, jets, and missing transverse momentum.
As in Ref.~\cite{Aad:2015pja}, $P^\textrm{sig}$ and $P^\textrm{bkg}$ are approximated as a product of one-dimensional pdfs for
each of the invariant masses considered, and averaged among all possible parton--jet matching combinations. 
Combinations are weighted using information on the per-jet multivariate $b$-tagging discriminant value to suppress the impact from 
parton--jet assignments that are inconsistent with the correct flavour of the parton candidates.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[htbp]
\begin{center}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_lep0_pt.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_met.eps}} \\
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_hthad.eps}} 
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Hbb/other_variables/c1lep4jex3bex_mbb_mindR.eps}} \\ 
\caption{\small{$\Hbb$ search: Comparison between the data and background prediction for several kinematic 
distributions in the (4j, 3b) region before the fit to data (``Pre-Fit''). 
The distributions are shown for (a) lepton $\pt$, (b) $\met$, (c) scalar sum of the transverse momenta of 
the jets ($\hthad$), and (d) the invariant mass of the two $b$-tagged jets with lowest 
$\Delta R$ separation ($\mbb$).
The small contributions from $\ttbar V$, $\ttbar H$, single-top-quark, $W/Z$+jets, diboson, and multijet backgrounds are combined 
into a single background source referred to as ``Non-$\ttbar$''. 
The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
added to the background prediction.
The last bin in all figures contains the overflow.
The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction. 
The blue triangles indicate points that are outside the vertical range of the figure. 
The hashed area represents the total uncertainty of the background, excluding the normalisation uncertainty of the $\ttbin$ background, 
which is determined via a likelihood fit to data.}}
\label{fig:Hbb_extravars_4j3b}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-11-14 sections/strategy_Htautau.tex
Partly implemented D. Stoker's CDS comments

In the $\Htautau$ search, the $\ttbar \to WbHq$ signal being probed is characterised by the presence of $\tau$-leptons from the decay of 
the Higgs boson and at least four jets, only one of which originates from a $b$-quark.
%In the $\Htautau$ search, the final state signature of interest is characterised by the presence of two $\tau$-leptons from the
%decay of the Higgs boson as well as a light-quark jet, the latter two originating from the decay of one of the top quarks. 
If one of the $\tau$-leptons decays leptonically, an isolated electron or muon and significant $\met$ is also expected.
%The other top quark decays into a $W$ boson and a $b$-quark, with the $W$ boson in turn decaying hadronically, resulting in 
%three additional jets. Therefore, at least four jets are typically expected in signal events.
However, in a significant fraction of the events the lowest-$\pt$ jet from the $W$-boson decay fails the minimum $\pt$ requirement of $30~\gev$,
resulting in signal events with only three jets reconstructed.
In order to optimise the sensitivity of the search, the selected events are categorised into four SRs depending 
on the number of $\taulep$ and $\had$ candidates, and on the number of jets:
($\lephad$, 3j), ($\lephad$, $\geq$4j), ($\hadhad$, 3j), and ($\hadhad$, $\geq$4j).

This event categorisation is primarily motivated by the different quality of the event kinematic reconstruction, depending on the amount 
of $\met$ in the event (larger in $\lephad$ events compared to $\hadhad$ events), and whether a jet from the hadronic top-quark decay 
is missing or not (events with exactly three jets or at least four jets).
%This analysis adopts the event reconstruction strategy developed in Ref.~\cite{Chen:2015nta}, which is briefly summarised in the following. 
%The event reconstruction strategy used~\cite{Chen:2015nta} is summarised in the following.
The event reconstruction is based on the strategy used in Ref.~\cite{Chen:2015nta}.

@@

%%%%%%%%%%%%%%%
\begin{table*}[t!]
\begin{center}
\begin{tabular}{ccccc}
\toprule\toprule 
& \multicolumn{2}{c}{$\lephad$} & \multicolumn{2}{c}{$\hadhad$} \\
Variable & 3j & $\geq$4j & 3j & $\geq$4j  \\
\midrule
$m_{\tau\tau}^{\text{fit}}$                      	& $\times$  & $\times$  & $\times$  & $\times$ \\
$m_{Hq}$                                	& $\times$  & $\times$  & $\times$  & $\times$ \\
$m_{\text{T,lep}}$                              	& $\times$  & $\times$  &             & \\
$p_{\text{T,1}}$                             	& $\times$  & $\times$ & $\times$  & $\times$ \\
$p_{\text{T,2}}$                             	& $\times$  & $\times$  & $\times$  & $\times$ \\
$\met$ $\phi$ centrality                             	& $\times$  & $\times$  & $\times$  & $\times$ \\
$E_{\text{T},\parallel}^{\text{miss}}$          	& $\times$  & $\times$  & $\times$  & $\times$ \\
$E_{\text{T},\perp}^{\text{miss}}$          	& $\times$  & $\times$  &             & \\
$m_{b j_1}$                   		        & $\times$  & $\times$  & $\times$  & $\times$ \\
$m_{\text{lep}j}$      			        & $\times$  & $\times$  &   	  & \\
$m_{\tau j}$      			        & $\times$  & $\times$  &   	  & \\
$x_1^{\text{fit}}$				& $\times$  &	$\times$  & $\times$  & $\times$ \\
$x_2^{\text{fit}}$				& $\times$  & $\times$  & $\times$  & $\times$ \\
$m_{b j_1 j_2 }$             	   		&             & $\times$  &             & $\times$ \\ 
%\hline
\bottomrule\bottomrule
\end{tabular}
\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for each search region (denoted by $\times$). 
The description of each variable is provided in the text.}}
\label{tab:mva_var}
\end{center}
\end{table*}
%%%%%%%%%%%%%%%

@@

\begin{itemize}
\item $m_{\tau\tau}^{\text{fit}}$: the invariant mass of the two $\tau$-lepton candidates after the reconstruction of the neutrinos, indicating the reconstructed Higgs boson mass.
\item $m_{Hq}$: the invariant mass of the reconstructed Higgs boson and the associated light-quark jet in the $t \to Hq$ decay, corresponding to the reconstructed mass of the parent top quark.
\item $m_{\text{T,lep}}$: the transverse mass calculated from the lepton and $\met$ in the $\lephad$ channel.
\item $p_{\text{T,1}}$ and $p_{\text{T,2}}$:  the transverse momenta of the lepton and $\had$ candidate (denoted as particles 1 and 2 respectively) in the $\lephad$ channel, or the transverse momenta of the leading and trailing $\had$ candidates (denoted as particles 1 and 2 respectively) in the $\hadhad$ channel.
\item $\met$ $\phi$ centrality: a variable that quantifies the relative angular position of the $\mpt$ with respect to the 
visible $\tau$-lepton decay products in the transverse plane. The transverse plane is transformed such that the direction of the $\tau$-lepton decay products are 
orthogonal, and that the smaller angle between the $\tau$-lepton decay products defines the positive quadrant of the transformed plane. 
The $\met$ $\phi$ centrality is defined as the sum of the $x$ and $y$ components of the $\mpt$ unit vector in this transformed plane.
%\item $E_{\text{T},\parallel}^{\text{miss}}$: the magnitude of the projection of $\mpt$ in the parallel direction in the transformed plane (see definition of $\met$ $\phi$ centrality).
%\item $E_{\text{T},\perp}^{\text{miss}}$: the magnitude of the projection of $\mpt$ in the transverse direction in the transformed plane (see definition of $\met$ $\phi$ centrality).
\item $E_{\text{T},\parallel}^{\text{miss}}$: the magnitude of the projection of the original $\mpt$ vector parallel to the fitted $\mpt$ vector, minus 
the magnitude of the fitted $\mpt$ vector.
\item $E_{\text{T},\perp}^{\text{miss}}$: the magnitude of the projection of the original $\mpt$ vector perpendicular to the fitted $\mpt$ vector.
\item $m_{b j_1}$: the invariant mass of the $b$-jet and the leading jet candidate from the hadronically decaying $W$ boson.
\item $m_{\text{lep}j}$: the invariant mass of the lepton and the jet that has the smallest angular distance to the $\lep$ candidate.
\item $m_{\tau j}$: the invariant mass of the  $\had$ candidate and the jet that has the smallest angular distance to the $\had$ candidate.
\item $x_{1}^{\text{fit}}$ and $x_{2}^{\text{fit}}$: the momentum fractions carried by the visible decay products from the two $\tau$-lepton candidates 
(whether $\taulep$ or $\had$) per event. It is based on the best-fit four-momentum of the neutrino(s) according to the event reconstruction procedure outlined in Section~\ref{sec:htautau_reco_cat}.
\item $m_{bj_1j_2}$: the invariant mass of the $b$-jet and the two jets originating from the $W$ boson in the $t\to Wb \to j_1j_2b$ decay, corresponding to the reconstructed mass of the parent top quark. This variable is only defined for events with at least four jets.
\end{itemize}

>>>>

In the $\Htautau$ search, the $\ttbar \to WbHq$ signal being probed is characterised by the presence of $\tau$-leptons from the decay of 
the Higgs boson and at least four jets, only one of which originates from a $b$-quark.
%In the $\Htautau$ search, the final state signature of interest is characterised by the presence of two $\tau$-leptons from the
%decay of the Higgs boson as well as a light-quark jet, the latter two originating from the decay of one of the top quarks. 
If one of the $\tau$-leptons decays leptonically, an isolated electron or muon and significant $\met$ is also expected.
%The other top quark decays into a $W$ boson and a $b$-quark, with the $W$ boson in turn decaying hadronically, resulting in 
%three additional jets. Therefore, at least four jets are typically expected in signal events.
However, in a significant fraction of the events the lowest-$\pt$ jet from the $W$ boson decay fails the minimum $\pt$ requirement of $30~\gev$,
resulting in signal events with only three jets reconstructed.
In order to optimise the sensitivity of the search, the selected events are categorised into four SRs depending 
on the number of $\taulep$ and $\had$ candidates, and on the number of jets:
($\lephad$, 3j), ($\lephad$, $\geq$4j), ($\hadhad$, 3j), and ($\hadhad$, $\geq$4j).

This event categorisation is primarily motivated by the different quality of the event kinematic reconstruction, depending on the amount 
of $\met$ in the event (larger in $\lephad$ events compared with $\hadhad$ events), and whether a jet from the hadronic top-quark decay 
is missing or not (events with exactly three jets or at least four jets).
%This analysis adopts the event reconstruction strategy developed in Ref.~\cite{Chen:2015nta}, which is briefly summarised in the following. 
%The event reconstruction strategy used~\cite{Chen:2015nta} is summarised in the following.
The event reconstruction is based on the strategy used in Ref.~\cite{Chen:2015nta}.

@@

%%%%%%%%%%%%%%%
\begin{table*}[t!]
\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for each search region (denoted by $\times$). 
The description of each variable is provided in the text.}}
\begin{center}
\begin{tabular}{ccccc}
\toprule\toprule 
& \multicolumn{2}{c}{$\lephad$} & \multicolumn{2}{c}{$\hadhad$} \\
Variable & 3j & $\geq$4j & 3j & $\geq$4j  \\
\midrule
$m_{\tau\tau}^{\text{fit}}$                      	& $\times$  & $\times$  & $\times$  & $\times$ \\
$m_{Hq}$                                	& $\times$  & $\times$  & $\times$  & $\times$ \\
$m_{\text{T,lep}}$                              	& $\times$  & $\times$  &             & \\
$p_{\text{T,1}}$                             	& $\times$  & $\times$ & $\times$  & $\times$ \\
$p_{\text{T,2}}$                             	& $\times$  & $\times$  & $\times$  & $\times$ \\
$\met$ $\phi$ centrality                             	& $\times$  & $\times$  & $\times$  & $\times$ \\
$E_{\text{T},\parallel}^{\text{miss}}$          	& $\times$  & $\times$  & $\times$  & $\times$ \\
$E_{\text{T},\perp}^{\text{miss}}$          	& $\times$  & $\times$  &             & \\
$m_{b j_1}$                   		        & $\times$  & $\times$  & $\times$  & $\times$ \\
$m_{\text{lep}j}$      			        & $\times$  & $\times$  &   	  & \\
$m_{\tau j}$      			        & $\times$  & $\times$  &   	  & \\
$x_1^{\text{fit}}$				& $\times$  &	$\times$  & $\times$  & $\times$ \\
$x_2^{\text{fit}}$				& $\times$  & $\times$  & $\times$  & $\times$ \\
$m_{b j_1 j_2 }$             	   		&             & $\times$  &             & $\times$ \\ 
%\hline
\bottomrule\bottomrule
\end{tabular}
\label{tab:mva_var}
\end{center}
\end{table*}
%%%%%%%%%%%%%%%

@@

\begin{itemize}
\item $m_{\tau\tau}^{\text{fit}}$: the invariant mass of the two $\tau$-lepton candidates after the reconstruction of the neutrinos, indicating the reconstructed Higgs boson mass.
\item $m_{Hq}$: the invariant mass of the reconstructed Higgs boson and the associated light-quark jet in the $t \to Hq$ decay, corresponding to the reconstructed mass of the parent top quark.
\item $m_{\text{T,lep}}$: the transverse mass calculated from the lepton and $\met$ in the $\lephad$ channel.
\item $p_{\text{T,1}}$ and $p_{\text{T,2}}$:  the transverse momenta of the lepton and $\had$ candidate (denoted as particles 1 and 2 respectively) in the $\lephad$ channel, or the transverse momenta of the leading and trailing $\had$ candidates (denoted as particles 1 and 2 respectively) in the $\hadhad$ channel.
\item $\met$ $\phi$ centrality: a variable that quantifies the angular position of the $\mpt$ relative to the 
visible $\tau$-lepton decay products in the transverse plane. The transverse plane is transformed such that the directions of the $\tau$-lepton decay products are 
orthogonal, and that the smaller angle between the $\tau$-lepton decay products defines the positive quadrant of the transformed plane. 
The $\met$ $\phi$ centrality is defined as the sum of the $x$ and $y$ components of the $\mpt$ unit vector in this transformed plane.
%\item $E_{\text{T},\parallel}^{\text{miss}}$: the magnitude of the projection of $\mpt$ in the parallel direction in the transformed plane (see definition of $\met$ $\phi$ centrality).
%\item $E_{\text{T},\perp}^{\text{miss}}$: the magnitude of the projection of $\mpt$ in the transverse direction in the transformed plane (see definition of $\met$ $\phi$ centrality).
\item $E_{\text{T},\parallel}^{\text{miss}}$: the magnitude of the projection of the original $\mpt$ vector parallel to the fitted $\mpt$ vector, minus 
the magnitude of the fitted $\mpt$ vector.
\item $E_{\text{T},\perp}^{\text{miss}}$: the magnitude of the projection of the original $\mpt$ vector perpendicular to the fitted $\mpt$ vector.
\item $m_{b j_1}$: the invariant mass of the $b$-jet and the leading jet candidate from the hadronically decaying $W$ boson.
\item $m_{\text{lep}j}$: the invariant mass of the lepton and the jet that has the smallest angular distance to the $\lep$ candidate.
\item $m_{\tau j}$: the invariant mass of the  $\had$ candidate and the jet that has the smallest angular distance to the $\had$ candidate.
\item $x_{1}^{\text{fit}}$ and $x_{2}^{\text{fit}}$: the momentum fractions carried by the visible decay products from the two $\tau$-lepton candidates 
(whether $\taulep$ or $\had$) per event. It is based on the best-fit four-momentum of the neutrino(s) according to the event reconstruction procedure outlined in Section~\ref{sec:htautau_reco_cat}.
\item $m_{bj_1j_2}$: the invariant mass of the $b$-jet and the two jets originating from the $W$ boson in the $t\to Wb \to j_1j_2b$ decay, corresponding to the reconstructed mass of the parent top quark. This variable is only defined for events with at least four jets.
\end{itemize}
